A thermodynamic view of dusty protoplanetary disks

### 2017-05-12 paper.tex
tiny wording changes to sec 2

\section{Dust-free modeling of dusty protoplanetary disks}\label{key_idea}
{\bf is this section needed?} 
The key concept we introduce in this work is the description 
of dusty protoplanetary disks \emph{without} explicit dust 
equations. This is best illustrated by writing down our model   
equations for a mixture of isothermal gas and small 
dust particles: 
\begin{align}  
  &\frac{\p \rho}{\p t} + \nabla\cdot\left(\rho\bm{v}\right)= 0, \label{mass0}\\ 
  &\frac{\p\bm{v}}{\p t} + \bm{v}\cdot\nabla\bm{v} = -
  \frac{1}{\rho}\nabla  P - \nabla \Phi_*,\label{mom0}\\ 
 & \frac{\p P}{\p t} + \bm{v}\cdot\nabla P 
  = - P \nabla\cdot\bm{v} - \nabla\cdot\bm{\mathcal{F}}
%                + \mathcal{C}(\rho, P; \tstop)
\label{en0}, 
\end{align}
where $\rho=\rhod + \rhog$ is the total density, $P$ is the pressure,
$\Phi_*$ is the stellar gravitational potential,   
and $\bm{\mathcal{F}}$ model effects of dust-gas drag, explained below. 
%$\mathcal{C}$ represent effects of dust-gas drag, which
%is paremterized by the stopping time $\tstop$ ($\mathcal{C}=0$ for
%$\tstop=0$). 
Similar equations for dusty-gas are given by
\cite{price15}.

Eq. \ref{mass0}---\ref{en0} appear identical to pure gas
dynamics, but they physically represents a two-phase, 
dusty gas. The mixture obeys mass and momentum conservation as usual,
but also an energy-like equation, even though the system is
isothermal by assumption. The term $\bm{\mathcal{F}}\propto -\tstop
\nabla P$ is not a true heat flux. Instead, it reflects 
particle flux towards pressure maximum due to dust-gas drag 
\citep{weidenschilling77}. The back-reaction onto the gas then changes
the pressure distribution.

>>>>

\section{Dust-free modeling of dusty protoplanetary disks}\label{key_idea}
{\bf is this section needed?} 
The key concept we introduce in this work is the description 
of dusty protoplanetary disks \emph{without} explicit dust 
equations. This is best illustrated by writing down our model   
equations for a mixture of isothermal gas and small 
dust particles: 
\begin{align}  
  &\frac{\p \rho}{\p t} + \nabla\cdot\left(\rho\bm{v}\right)= 0, \label{mass0}\\ 
  &\frac{\p\bm{v}}{\p t} + \bm{v}\cdot\nabla\bm{v} = -
  \frac{1}{\rho}\nabla  P - \nabla \Phi_*,\label{mom0}\\ 
 & \frac{\p P}{\p t} + \bm{v}\cdot\nabla P 
  = - P \nabla\cdot\bm{v} - \nabla\cdot\bm{\mathcal{F}}
%                + \mathcal{C}(\rho, P; \tstop)
\label{en0}, 
\end{align}
where $\rho=\rhod + \rhog$ is the total density, $P$ is the pressure,
$\Phi_*$ is the stellar gravitational potential,   
and $\bm{\mathcal{F}}=~\bm{\mathcal{F}}(\rho, P; \tstop)$ model effects of dust-gas drag, explained below. 
%$\mathcal{C}$ represent effects of dust-gas drag, which
%is paremterized by the stopping time $\tstop$ ($\mathcal{C}=0$ for
%$\tstop=0$). 
Similar equations for dusty-gas are given by
\cite{price15}.

Eq. \ref{mass0}---\ref{en0} appear identical to pure gas
dynamics, but they physically represents a two-phase, 
dusty gas. The mixture obeys mass and momentum conservation as usual,
but also an energy-like equation, even though the system is
isothermal by assumption. The term $-\bm{\mathcal{F}}\propto \tstop
\nabla P$ is not a true heat flux. Instead, it reflects 
particle flux towards pressure maximum due to dust-gas drag 
\citep{weidenschilling77}. The back-reaction onto the gas then changes
the pressure distribution.
